\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-28 paper/intersection.tex
Fixing bug in intersection.tex

As described in Section~\ref{sec-intro} and in~\cite{sff-foci2014}, the FBI used
set intersection to search for phone numbers that appeared in three sets of
cell-tower dumps. This procedure did not follow the the openness principle.
The FBI did not distinguish between targeted and untargeted users when
collecting the data. It only arrested the user in the intersection of the sets
it collected, as far as we know, but as there was no established accountability
procedure, we do not know whether the FBI retained the phone numbers of
untargeted users collected during the search, whether it subjected any of those
other phone numbers to additional investigation, whether it shared the data sets
of 150,000 total users with other government agencies, \it{etc}.

Segal \it{et al.}~\cite{sff-foci2014} presented a private set intersection
protocol to address these specific concerns. We present a summary of that protocol
in Section~\ref{sec-isectproto}. This protocol reveals \emph{only} the identities
of users in the intersection of the sets under consideration, leaving the other,
untargeted users' identities hidden by encryption. To provide accountability and
oversight, the protocol requires multiple government agencies to participate. This
provides a division of authority. No one agency can uncover users' identities
without other agencies being able to collect records about how often intersection
warrants are used and set restrictions on how many users the agencies can identify
under a single warrant.

>>>>

As described in Section~\ref{sec-introduction} and in~\cite{sff-foci2014}, the FBI used
set intersection to search for phone numbers that appeared in three sets of
cell-tower dumps. This procedure did not follow the the openness principle.
The FBI did not distinguish between targeted and untargeted users when
collecting the data. It only arrested the user in the intersection of the sets
it collected, as far as we know, but as there was no established accountability
procedure, we do not know whether the FBI retained the phone numbers of
untargeted users collected during the search, whether it subjected any of those
other phone numbers to additional investigation, whether it shared the data sets
of 150,000 total users with other government agencies, \emph{etc}.

Segal \emph{et al.}~\cite{sff-foci2014} presented a private set intersection
protocol to address these specific concerns. We present a summary of that protocol
in Section~\ref{sec-isectproto}. This protocol reveals \emph{only} the identities
of users in the intersection of the sets under consideration, leaving the other,
untargeted users' identities hidden by encryption. To provide accountability and
oversight, the protocol requires multiple government agencies to participate. This
provides a division of authority. No one agency can uncover users' identities
without other agencies being able to collect records about how often intersection
warrants are used and set restrictions on how many users the agencies can identify
under a single warrant.
